Structured Versus Decorated Cospans

### 2020-11-17 cospans.tex
polished material around Theorem 2.3

The remaining properties are coherence diagrams that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $\alpha,\lambda,\rho$ and $\beta$ and the double category structure functors $U$ and $\odot$. We exhibit one of these diagrams to give the reader a sense of how they are verified, with more details able to be found in the second author's thesis \cite{CourserThesis}. The coherence diagram that we will check is given by:
The remaining properties are coherence laws that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $\alpha,\lambda,\rho$ and $\beta$ and the double category structure functors $U$ and $\odot$. We exhibit one of these laws to give the reader a sense of how they are verified, with more details available in the second author's thesis \cite{CourserThesis}. The coherence law that we check says that this diagram commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$};
\node (B) at (3,0) {$(N_1 \odot N_2) \otimes (M_1 \odot M_2)$};
\node (C) at (0,-.75) {$(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$};
\node (D) at (3,-.75) {$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\beta$} (B)
(B) edge node[right]{$\chi$} (D)
(A) edge node[left]{$\chi$} (C)
(C) edge node[above]{$\beta \odot \beta$} (D);
\end{tikzpicture}
\]
which expresses that the braiding is a transformation of double categories.

@@

@@

@@

@@

@@

>>>>

The remaining properties are coherence diagrams that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $\alpha,\lambda,\rho$ and $\beta$ and the double category structure functors $U$ and $\odot$. We exhibit one of these diagrams to give the reader a sense of how they are verified, with more details able to be found in the second author's thesis \cite{CourserThesis}. The coherence diagram that we will check is given by:
The remaining properties are coherence laws that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $\alpha,\lambda,\rho$ and $\beta$ and the double category structure functors $U$ and $\odot$. We exhibit one of these laws to give the reader a sense of how they are verified, with more details available in the second author's thesis \cite{CourserThesis}. The coherence law that we check says that this diagram commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$};
\node (B) at (3,0) {$(N_1 \odot N_2) \otimes (M_1 \odot M_2)$};
\node (C) at (0,-.75) {$(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$};
\node (D) at (3,-.75) {$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\beta$} (B)
(B) edge node[right]{$\chi$} (D)
(A) edge node[left]{$\chi$} (C)
(C) edge node[above]{$\beta \odot \beta$} (D);
\end{tikzpicture}
\]
which expresses that the braiding is a transformation of double categories.
This expresses that the braiding is a transformation of double categories.

@@

Our construction gives not only decorated cospan double categories, but maps betwen these.
Suppose we have two symmetric lax monoidal pseudofunctors, $F \maps \A \to \Cat$ and
$F' \maps \A' \to \Cat$.    Then we can obtain a map between their decorated cospan 
double categories, $\lH \maps F\lCsp \to F' \lCsp$, from:
\begin{itemize}
\item a finitely cocontinous functor $H \maps \A \to \A'$, 
\item a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$, 
\item an isomorphism $\theta \maps EF \Rightarrow F'H$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\A$};
\node (B) at (1,0) {$\Cat$};
\node (C) at (0,-1) {$\A'$};
\node (D) at (1,-1) {$\Cat$.};
\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F$} (B)
(A) edge node[left]{$H$} (C)
(B) edge node[right]{$E$} (D)
(C) edge node[above]{$F'$} (D);
\end{tikzpicture}
\]
\end{itemize}

@@

\node (D) at (2,-0.5) {$\lH(M \odot N) = \theta_{c_1 +_b c_2}E(d_{M \odot N}) \phi \in F'(H(c_1 +_b c_2))$};

@@

where $$\lH(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \maps 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F'(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\lH$ is given respectively by $\lH(M)$ and $\lH(N)$:

@@

\node (E) at (7.5,0.5) {$d_{\lH(M) \odot \lH(N)} \in F'(H(c_1)+_{H(b_1)}H(c_2))$};
\node (F) at (7.5,-0.5) {$d_{\lH(M \odot N)} \in F'(H(c_1 +_b c_2))$};
\node (G) at (2.5,-1) {$\tau_{\kappa^{-1}} \maps F'(\kappa^{-1})(d_{\lH(M) \odot \lH(N)}) \to d_{\lH(M \odot N)}.$};

@@

where $\kappa$ is the isomorphism $$\kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \maps \A \to \A'$. The above diagram commutes by a similar argument to the one used in \cref{thm:equiv}. Similarly, for every object $c \in \A$, we have a unit comparison constraint $$\lH_U \maps U_{\lH(c)} \to \lH(U_c)$$ given by the globular 2-isomorphism:
